Dirac neutrino mass generation from Majorana messenger

### 2019-09-14 draft.tex
wrong caption

@@

    \mathcal{L} \supset& -[ 
    h_{i\alpha} \overline{L_{i}} \tilde{\eta} \psi_{R\alpha} +  y_{j\alpha} \overline{\nu_{R_{j}}} \sigma^* \psi^c_{R\alpha} + \kappa_{\alpha\beta} \overline{\psi^{c}_{R\alpha}} \psi_{R\beta} S^* + \text{h.c.}] - \mathcal{V}(H, S, \eta, \sigma)\,,

@@

where $L_{i}$ ($i=1,2,3$) and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^*$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 

@@

\section{Neutrino masses and charged lepton flavor violation}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{Neutrino_Loop.pdf}
\caption{One-loop realization of the dimension-6 operator $\overline{L} \tilde{H} \nu_R S^2$ leading to Dirac neutrino masses with Majorana mediators.}
\label{fig:zee}
\end{figure}
%
Thanks to the scalar mixing term $\lambda_8$ nonzero Dirac neutrino masses are generated at one-loop level according to the diagram in  Fig.~\ref{fig:zee}. The expression for the effective neutrino mass matrix $\mathcal{M}_{\nu}$ can be cast as
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S^2 v_H} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} \kappa_\alpha y^{*}_{j\alpha}\left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
%(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S v_H} %{m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} %M_{\psi_{\alpha}}y^{*}_{j\alpha}\left[ F\left( %\frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( %\frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
\end{align}
%
%check the following formula:
where $F(x) =x \log x/(x-1)$ and $M_{\psi_\alpha}=\kappa_{\alpha}v_S$ has been used once. 
%, $M_{\psi_{a}}$ is
%the fermion mass and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the
%two CP-even (CP-odd) mass eigenstates.
%It follows that to obtain nonzero neutrino masses it is necessary that $\mu\equiv\lambda_8 %v_S \neq 0$. 
Note that the structure of the effective neutrino mass matrix, given by the
product $(M_{\nu})_{ij} \propto h_{i \alpha} y_{j\alpha}$, is similar to
the structure of the neutrino mass matrix for the tree-level seesaw
mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. 
It is also worth mentioning that if only one
fermion $\psi_R$ is added, then there will be two massless neutrinos, which
would be ruled out by the current neutrino oscillation data~\cite{deSalas:2017kay}. 
In our case, we assume the
existence of three of such fermions, generating Dirac scotogenic masses for
the two left-handed neutrinos ($\nu_{3}=\nu_{L3}+\nu_{R3}$ is massless due to the charge assignment).

@@

%\section{Lepton flavor violation}
%\label{sec:LFV}
%
\begin{figure}
\centering
\includegraphics[scale=0.75]{LFV.pdf}
\caption{Feynman diagram for the processes $\ell_{i} \to \ell_{j} \gamma$}
\label{fig:LFV}
\end{figure}
%
On the other hand, the $h_{i\alpha}$ Yukawa interaction in Eq.~\eqref{eq:LagY} leads to charged lepton flavor violation (CLFV) processes induced at one-loop level and mediated by the charged scalars $\eta^{\pm}$) as the ones shown in Fig.~\ref{fig:LFV} for the $\ell_i\to\ell_j\gamma$ type. 
current experimental constraint on Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\cite{Adam:2013mnn} and for the case $m_\chi^2=m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$
 we obtain an upper bound for the Yukawa couplings product (for a given $m_\chi$)
\begin{align}
    \left| \sum_{\alpha}h_{i \alpha} h_{j\alpha}^{*} \right| \lesssim 0.02 \left(\frac{m_\chi}{2\,\text{TeV}} \right)^{2}.
\end{align}
It is worth noticing that $y_{j\alpha}$ is not constrained by the non observation of LFV processes. 
%
%which leads to a very slight requirement,

@@

%\subsection{Fermion dark matter}
Since $\psi_{1}$ is a singlet under the SM gauge group its thermal relic density is controlled by the Yukawa and $\operatorname{U}(1)_X$ gauge interactions. 
The scenario where $\psi_{1}$ self-annihilates dominantly through $h_{i\alpha}$-mediated interactions resembles the very well known scotogenic model \cite{Ma:2006km},  
where sizable $h_{i\alpha}$ are required to reproduce the correct DM abundance, which in turn leads to a mild tension with experimental upper bounds on the rates for rare charged lepton decays~\cite{Kubo:2006yx,Sierra:2008wj,Ibarra:2016dlb}. 
%The phenomenology of this scenario has been extensively studied  \cite{Kubo:2006yx,Sierra:2008wj,Suematsu:2009ww,Gelmini:2009xd,Hambye:2009pw,Aoki:2010tf,Schmidt:2012yg,Ma:2012if,Kashiwase:2012xd,Kashiwase:2013uy,Racker:2013lua,Toma:2013zsa,Molinaro:2014lfa,Vicente:2014wga,Merle:2015gea,Merle:2015ica,Merle:2016scw,Hagedorn:2016dze,Lindner:2016kqk,Hessler:2016kwm,Ibarra:2016dlb}.
On the other hand, when the $Z'$ portal \cite{Langacker:2008yv,Dudas:2009uq} is the main gate to visible sector, $\psi_1$ largely annihilates into neutrinos in such a way the observed DM abundance can be reproduced without entering in conflict with the DM searches, which follows from the fact that the $Z'$ does not couples to quarks neither to charged leptons)
(see~\cite{Dudas:2009uq,Arcadi:2013qia,Alves:2013tqa,Alves:2015pea,Alves:2016cqf,Blanco:2019hah} for related phenomenological studies on $Z'$-mediated Majorana DM). 
% check Ibarra papers
%also through the annihilation
%$\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via 
%Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted by
%CLFV and neutrino masses. %But, Yukawa couplings $y^{a}_{j}$ is free.
%In the case where the mass of the other fermions and scalars is nearly
%degenerated to $\psi_{1} $, the processes of coannihilation can be
%relevant for the relic density calculation~\cite{Klasen:2013jpa}.

@@

%\subsection{Scalar dark matter}
In contrast to fermion DM, the scalar DM candidate has additional interaction terms to the Yukawa and gauge interactions. This entails that the later ones can be used to alter the relic density predictions in scenarios with mixed scalar DM. Since in the present model the CP-even and CP-odd neutral $Z_2$-odd particles are mass degenerate, we have the scenario of singlet-doublet complex DM~\cite{Kadastik:2009dj,Belanger:2012vp} where the DM candidate is a mixture of a complex singlet \cite{McDonald:1993ex} and a $SU(2)_L$ doublet \cite{Deshpande:1977rw,Barbieri:2006dq}. It follows that for negligible Yukawa and gauge interactions there are two DM mass regions that allow us to properly reproduce the relic abundance, one corresponds the Higgs funnel region and the second one lies above $100$ GeV~\cite{Kakizaki:2016dza}.

@@

\section{Cosmological constraints}
\label{sec:CosmoConstraints}
A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM. The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}
There are many known solutions for the case in which $e-2l=1$. The full set of standard model charges in terms of $l$ is just
\begin{align}
  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
  \label{Eq:SMCharges}
\end{align}
The same solution but in terms of $h$ is given in ~\cite{Okada:2018tgy}.

@@

%the charges for the SM particles are in equations~\ref{Eq:SMCharges}. Since these are determined by the anomaly cancellation equations.
%For this operator we have that the charges for the new particles are given by
%\begin{align}
%    \psi=&-\frac{\nu+1}{4}\,,&\eta=&-\frac{\nu+1}{4}-l\,,&\sigma=&\frac{1-3\nu}{4}\,.
%\end{align}
%As we are interested here in the case of the exotic set of X-charges charges:$\mp 4$,$\mp 4$,$\pm 5$, the charges for the model particles are shown in the table~\ref{tab:partcont3}.
%Because the charges of the SM fermions are the same for both operators ($5d$ and $6d$), the $N_{eff}$ restrictions shown in the figure~\ref{fig:Neff} apply to both operators.
%
\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline  
    Fields     & $\operatorname{SU}(2)_L$ & $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_R$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
$L $  & $\boldsymbol{2}$& $-1/2$  &  $l$&  $-1$&    $0$ &  $-3/2$&  $-1/2$ \\    
$d_R $  & $\boldsymbol{1}$& $-1/2$  &  $1+2l/3$&  $1/3$&    $1$&  $0$&  $2/3$ \\
$u_R $  & $\boldsymbol{1}$& $+2/3$  &  $-1-4l/3$&  $1/3$&   $-1$&  $1$&  $-1/3$ \\
$Q $  & $\boldsymbol{2}$& $-1/6$  &  $-l/3$& $1/3$&    $0$&  $1/2$&  $1/6$ \\\hline
$e_R $  & $\boldsymbol{1}$& $-1$  &  $1+2l$&  $-1$&    $1$ &  $-2$&  $0$ \\
$H $  & $\boldsymbol{2}$& $1/2$  &  $-1-l$&  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
$\eta$  & $\boldsymbol{2}$ & $+1/2$  & $3/4-l$& $7/4$& $3/4$ &$9/4$&$5/4$ \\
$S$ & $\boldsymbol{1}$ & $0$  & $3/2$& $3/2$&  $3/2$ & $3/2$& $3/2$ \\
$\sigma$ & $\boldsymbol{1}$ & $0$ & $13/4$& $13/4$&  $13/4$ & $13/4$& $13/4$ \\
\hline
 $\nu_{Ri}$ & $\boldsymbol{1}$ & $0$ & $-4$& $-4$&  $-4$ & $-4$& $-4$\\
$\nu_{R3}$ & $\boldsymbol{1}$ & $0$ & $+5$& $+5$&  $5$ & $5$& $5$\\
$\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$& $3/4$ & $3/4$&  $3/4$ & $3/4$& $3/4$ \\\hline
$\xi_{L\alpha}$  & $\boldsymbol{1}$ & $0$ & $3/4$& $3/4$ &  $3/4$ & $3/4$& $3/4$\\\hline
  \end{tabular}
  \caption{The new scalars and fermions with their respective charges for the 6-dimensional operator. The SM fields have the usual $U(1)_{B-L}$ assignment. Now $\alpha=1,2$}
    \label{tab:partcont3}
\end{table}
%

@@

\section{Collider constraints}
ATLAS~\cite{}
recasting~\cite{}
In fig.~\ref{fig:u1blc}...

@@

In the $\operatorname{U}(1)_{B-L}$, cosmlogical constraints are better that current ATLAS limit for $M_{Z'}\gtrsim 4.8\ \text{TeV}$

>>>>

\begin{align}

@@

    \mathcal{L} \supset& -\,g_{X}\,Z_\mu^\prime\sum_{F}q_{F}\overline{F} \gamma^\mu F+\sum_{\phi}\left|\left( \partial_\mu +i\,g_{X}\,q_\phi\,Z'_\mu \right) \phi\right|^2\nonumber\\
    &-[ 
    h_{i\alpha} \overline{L_{i}} \tilde{\eta} \psi_{R\alpha} +  y_{j\alpha} \overline{\nu_{R_{j}}} \sigma^* \psi^c_{R\alpha} + \kappa_{\alpha\beta} \overline{\psi^{c}_{R\alpha}} \psi_{R\beta} S^* + \text{h.c.}] - \mathcal{V}(H, S, \eta, \sigma)\,.
\end{align}

@@

In the first row $g_{X}$ is the gauge coupling associated to the $\operatorname{U}(1)_X$ group and $Z_\mu^\prime$ is its corresponding gauge boson, $F$ and $\phi$ denote the new chiral fermions and new scalars respectively, and $q_{F,\,\phi}$ their $X$ charges. In the second row
$L_{i}$ ($i=1,2,3$) and $H$ are the SM lepton and Higgs doublets, respectively,  $\widetilde{\eta} = i \sigma_2 \eta^*$, and $h$, $y$ and $\kappa$ are matrices in the flavor space. 

@@

\section{Neutrino masses and charged lepton flavor violation}
\label{sec:Neutrinos}
%
\begin{figure}
\centering
\includegraphics[scale=0.6]{Neutrino_Loop.pdf}
\caption{One-loop realization of the dimension-6 operator $\overline{L} \tilde{H} \nu_R S^2$ leading to Dirac neutrino masses with Majorana mediators.}
\label{fig:zee}
\end{figure}
%
Thanks to the scalar mixing term $\lambda_8$ nonzero Dirac neutrino masses are generated at one-loop level according to the diagram in  Fig.~\ref{fig:zee}. The expression for the effective neutrino mass matrix $\mathcal{M}_{\nu}$ can be cast as
%
\begin{align}
(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S^2 v_H} {m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} \kappa_\alpha y^{*}_{j\alpha}\left[ F\left( \frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( \frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
%(\mathcal{M}_{\nu})_{ij} = \frac{1}{64 \pi^{2}}  \frac{\lambda_8 v_S v_H} %{m_{\chi_{R_2}}^{2}-m_{\chi_{R_1}}^{2}}\sum_{\alpha=1}^{3} h_{i \alpha} %M_{\psi_{\alpha}}y^{*}_{j\alpha}\left[ F\left( %\frac{m_{\chi_{R_2}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) - F\left( %\frac{m_{\chi_{R_1}}^{2}}{M_{\psi_{\alpha}}^{2}} \right) \right] + (R \to I)\,,
\end{align}
%
%check the following formula:
where $F(x) =x \log x/(x-1)$ and $M_{\psi_\alpha}=\kappa_{\alpha}v_S$ has been used once. 
%, $M_{\psi_{a}}$ is
%the fermion mass and $\chi_{R_{(1,2)}}$ ( $\chi_{I_{(1,2)}}$ ) are the
%two CP-even (CP-odd) mass eigenstates.
%It follows that to obtain nonzero neutrino masses it is necessary that $\mu\equiv\lambda_8 %v_S \neq 0$. 
Note that the structure of the effective neutrino mass matrix, given by the
product $(M_{\nu})_{ij} \propto h_{i \alpha} y_{j\alpha}$, is similar to
the structure of the neutrino mass matrix for the tree-level seesaw
mechanism for Dirac neutrinos~\cite{Chulia:2016ngi}. 
It is also worth mentioning that if only one
fermion $\psi_R$ is added, then there will be two massless neutrinos, which
would be ruled out by the current neutrino oscillation data~\cite{deSalas:2017kay}. 
In our case, we assume the
existence of three of such fermions, generating Dirac scotogenic masses for
the two left-handed neutrinos ($\nu_{3}=\nu_{L3}+\nu_{R3}$ is massless due to the charge assignment).

@@

%\section{Lepton flavor violation}
%\label{sec:LFV}

On the other hand, the $h_{i\alpha}$ Yukawa interaction in Eq.~\eqref{eq:LagY} leads to charged lepton flavor violation (CLFV) processes induced at one-loop level and mediated by the charged scalars $\eta^{\pm}$) as the ones shown in Fig.~\ref{fig:LFV} for the $\ell_i\to\ell_j\gamma$ type. 
current experimental constraint on Br$(\mu \to e\gamma)$ \textless $5.7 \times 10^{-13} $~\cite{Adam:2013mnn} and for the case $m_\chi^2=m_{\eta^{\pm}}^{2} \gg M_{\psi_{a}}^{2}$
 we obtain an upper bound for the Yukawa couplings product (for a given $m_\chi$)
\begin{align}
    \left| \sum_{\alpha}h_{i \alpha} h_{j\alpha}^{*} \right| \lesssim 0.02 \left(\frac{m_\chi}{2\,\text{TeV}} \right)^{2}.
\end{align}
It is worth noticing that $y_{j\alpha}$ is not constrained by the non observation of LFV processes.

%
\begin{figure}[t]
\centering
\includegraphics[scale=0.6]{LFV.pdf}
\caption{Feynman diagram for the processes $\ell_{i} \to \ell_{j} \gamma$}
\label{fig:LFV}
\end{figure}
%

%
%which leads to a very slight requirement,

@@

%\subsection{Fermion dark matter}
Since $\psi_{1}$ is a singlet under the SM gauge group its thermal relic density is controlled by the Yukawa and $\operatorname{U}(1)_X$ gauge interactions. 
The scenario where $\psi_{1}$ self-annihilates dominantly through $h_{i\alpha}$-mediated interactions resembles the very well known scotogenic model \cite{Ma:2006km},  
where sizable $h_{i\alpha}$ are required to reproduce the correct DM abundance, which in turn leads to a mild tension with experimental upper bounds on the rates for rare charged lepton decays~\cite{Kubo:2006yx,Sierra:2008wj,Ibarra:2016dlb}. 
%The phenomenology of this scenario has been extensively studied  \cite{Kubo:2006yx,Sierra:2008wj,Suematsu:2009ww,Gelmini:2009xd,Hambye:2009pw,Aoki:2010tf,Schmidt:2012yg,Ma:2012if,Kashiwase:2012xd,Kashiwase:2013uy,Racker:2013lua,Toma:2013zsa,Molinaro:2014lfa,Vicente:2014wga,Merle:2015gea,Merle:2015ica,Merle:2016scw,Hagedorn:2016dze,Lindner:2016kqk,Hessler:2016kwm,Ibarra:2016dlb}.
On the other hand, when the $Z'$ portal \cite{Langacker:2008yv,Arcadi:2013qia} is the main gate to visible sector, $\psi_1$ largely annihilates into neutrinos in such a way the observed DM abundance can be reproduced without entering in conflict with the DM searches, which follows from the fact that the $Z'$ does not couples to quarks neither to charged leptons)
(see~\cite{Arcadi:2013qia,Alves:2013tqa,Alves:2015pea,Alves:2016cqf,Blanco:2019hah} for phenomenological studies on $Z'$-mediated Majorana DM). 
% check Ibarra papers
%also through the annihilation
%$\psi_{1} \psi_{1} \to l _{\alpha}^+ \overline{l}_{\beta}^- $, via 
%Yukawa coupling $h^{a}_{i}$. These Yukawa couplings are restricted by
%CLFV and neutrino masses. %But, Yukawa couplings $y^{a}_{j}$ is free.
%In the case where the mass of the other fermions and scalars is nearly
%degenerated to $\psi_{1} $, the processes of coannihilation can be
%relevant for the relic density calculation~\cite{Klasen:2013jpa}.

@@

%\subsection{Scalar dark matter}
In contrast to fermion DM, the scalar DM candidate has additional interaction terms to the Yukawa and gauge interactions. This entails that the later ones can be used to alter the relic density predictions in scenarios with mixed scalar DM. Since in the present model the CP-even and CP-odd neutral $Z_2$-odd particles are mass degenerate, we have the scenario of singlet-doublet complex DM~\cite{Kadastik:2009dj,Belanger:2012vp} where the DM candidate is a mixture of a complex singlet \cite{McDonald:1993ex} and a $SU(2)_L$ doublet \cite{Deshpande:1977rw,Barbieri:2006dq}. It follows that for negligible Yukawa and gauge interactions there are two DM mass regions that allow us to properly reproduce the relic abundance, one corresponds the Higgs funnel region and the second one demands masses above $100$ GeV~\cite{Kakizaki:2016dza}.

@@

\section{Beyond the minimal model: cosmological constraints}
\label{sec:CosmoConstraints}
A not-so-minimal model can be obtained by introducing additional chiral SM singlet fields. 
In this case we can use the solutions to the anomaly cancellation conditions found for an Abelian gauge symmetry $\operatorname{U(1)_X}$ in~\cite{Jenkins:1987ue,Appelquist:2002mw,Campos:2017dgc,Okada:2018tgy,Jana:2019mez}.
We use $f$ ($f$) to denote the $X$-charge of the field $f_R$ ($F_L$) for one generation of the SM. The three linear anomalies in $\operatorname{U(1)_X}$ allows to express three $X$-charges in terms of the other two
\begin{align}
  u=&-e+\frac{2l}{3}\,,& d=& e-\frac{4l}{3}\,,& q=& -\frac{l}{3}\,.
\end{align}
The quadratic anomaly condition is automatically satisfied, while the mixed gauge-gravitational and cubic anomalies depend of any extra singlet quiral fermions of zero hypercharge, like the right-handed counterpart of the Dirac neutrinos. For $\alpha$ extra quiral fields with $X$-charge $n_{\alpha}$, these conditions read
\begin{align}
  \sum_{\alpha} n_{\alpha}+3 (e-2l)=&0\,, &   \sum_{\alpha} n_{\alpha}^3+3 (e-2l)^3=&0\,. &
\end{align}
There are many known solutions for the case in which $e-2l=1$. The full set of standard model charges in terms of $l$ is just
\begin{align}
  u=&-1-\frac{4l}{3}\,,&d=&1+\frac{2l}{3}\,,&q=&-\frac{l}{3}\,,&e=&1+2l\,,&h=&-1-l\,.
  \label{Eq:SMCharges}
\end{align}
The same solution but in terms of $h$ is given in ~\cite{Okada:2018tgy}.

@@

%the charges for the SM particles are in equations~\ref{Eq:SMCharges}. Since these are determined by the anomaly cancellation equations.
%For this operator we have that the charges for the new particles are given by
%\begin{align}
%    \psi=&-\frac{\nu+1}{4}\,,&\eta=&-\frac{\nu+1}{4}-l\,,&\sigma=&\frac{1-3\nu}{4}\,.
%\end{align}
%As we are interested here in the case of the exotic set of X-charges charges:$\mp 4$,$\mp 4$,$\pm 5$, the charges for the model particles are shown in the table~\ref{tab:partcont3}.
%Because the charges of the SM fermions are the same for both operators ($5d$ and $6d$), the $N_{eff}$ restrictions shown in the figure~\ref{fig:Neff} apply to both operators.
%
\begin{table}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|c|c|}
    \hline  
    Fields     & $\operatorname{SU}(2)_L$ &  $\operatorname{U}(1)_Y $ & $\operatorname{U}(1)_{X}$& $\operatorname{U}(1)_{B-L}$& $\operatorname{U}(1)_R$& $\operatorname{U}(1)_D$& $\operatorname{U}(1)_G$\\ \hline
$L $     & $\boldsymbol{2}$ & $-1/2$ & $l$      &  $-1$&    $0$ &  $-3/2$&  $-1/2$ \\    
$d_R $   & $\boldsymbol{1}$ & $-1/2$ & $1+2l/3$ &  $1/3$&    $1$&  $0$&  $2/3$ \\
$u_R $   & $\boldsymbol{1}$ & $+2/3$ & $-1-4l/3$&  $1/3$&   $-1$&  $1$&  $-1/3$ \\
$Q $     & $\boldsymbol{2}$ & $-1/6$ & $-l/3$   & $1/3$&    $0$&  $1/2$&  $1/6$ \\\hline
$e_R $   & $\boldsymbol{1}$ & $-1$   & $1+2l$   &  $-1$&    $1$ &  $-2$&  $0$ \\
$H $     & $\boldsymbol{2}$ & $1/2$  & $-1-l$   &  $0$&    $-1$ &  $1/2$&  $-1/2$ \\
$\eta$   & $\boldsymbol{2}$ & $+1/2$ & $3/4-l$  & $7/4$& $3/4$ &$9/4$&$5/4$ \\
$S$      & $\boldsymbol{1}$ & $0$    & $3/2$    & $3/2$&  $3/2$ & $3/2$& $3/2$ \\
$\sigma$ & $\boldsymbol{1}$ & $0$    & $13/4$   & $13/4$&  $13/4$ & $13/4$& $13/4$ \\\hline
$\nu_{Ri}$& $\boldsymbol{1}$ & $0$   & $-4$& $-4$&  $-4$ & $-4$& $-4$\\
$\nu_{R3}$& $\boldsymbol{1}$ & $0$   & $+5$& $+5$&  $5$ & $5$& $5$\\
$\psi_{R\alpha}$  & $\boldsymbol{1}$ & $0$& $3/4$ & $3/4$&  $3/4$ & $3/4$& $3/4$ \\\hline
$\xi_{L\alpha}$   & $\boldsymbol{1}$ & $0$ & $3/4$& $3/4$ &  $3/4$ & $3/4$& $3/4$\\\hline
  \end{tabular}
  \caption{The new scalars and fermions with their respective charges for the 6-dimensional operator. The SM fields have the usual $U(1)_{B-L}$ assignment. Now $\alpha=1,2$}
    \label{tab:partcont3}
\end{table}
%

@@

\section{Collider constraints}
The recasting of the latest ATLAS results for the search of dilepton resonances using $139\ \text{fb}^{-1}$~\cite{1903.06248} was done
in~\cite{1903.06248} for the $\operatorname{U}(1)_{B-L}$ model.
The green region in Fig.~\ref{fig:u1blc} shows the excluded region at $95\%\ \text{C.L.}$. To ease the comparison with other results, we show the exclusion as function of $M_{Z'}/g_{BL}$. In particular, the limit from LEP for $\operatorname{U}(1)_{B-L}$ model is~\cite{1408.6845}, 
\begin{align}
  M_{Z'}/g_{BL}>6.7\ \text{TeV}\,,&&\text{at $95\%$ C.L }
\end{align}

which is obtained from the search for effective four-lepton operators and valid for $M_{Z'}\gg 200\ \text{GeV}$. This constraint is relevant for $M_{Z'}>5.8\ \text{TeV}$, is shown in the excluded magenta region.

@@

The constraint of $\Delta N_{\text{eff}}$ for $\operatorname{U}(1)_{B-L}$ is shown in the blue region and start to be better that current ATLAS limit for $M_{Z'}\gtrsim 4.8\ \text{TeV}$. Similar restrictions can be obtained for other values for the other models quoted in fig.~\ref{fig:Neff}.
